---
title: "Dynamic Model - Identification"
author: "Antonio Huerta Montellano"
date: "\today"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(comment = NA)
options(warn = FALSE) # ignore warnings
```

```{r libraries, include=FALSE}
library(lmtest) # for robust standard errors
library(dplyr) # for group_by function
library(ggplot2) # for better plots
library(dplyr) # for data managment
library(clubSandwich) # Grouped errors
library(sandwich) # MOre error options
library(tidyr) # Datframes manipulation
library(stargazer) # For output formats
library(lubridate)
library(plm)
```

```{r import_panel, include = FALSE, warning = FALSE}
setwd("C:/Users/metal/Documents/Github/MLB_hardball_negotations/")
hitters_panel <- read.csv('ETL_Data/Panel/Cumulative/Dynamic_model/panel_hitters_t_1.csv')
fielders_panel <- read.csv('ETL_Data/Panel/Cumulative/Dynamic_model/panel_fielders_t_1.csv')
```

```{r etl_panel, include = FALSE, warning = FALSE}
# Convert categorical column to numerical
# Position;
hitters_panel$position_num_t <- as.numeric(factor(hitters_panel$Posicion_t))
fielders_panel$position_num_t <- as.numeric(factor(fielders_panel$Posicion_t))
# Team:
hitters_panel$team_num_t <- as.numeric(factor(hitters_panel$Acronimo_t))
fielders_panel$team_num_t <- as.numeric(factor(fielders_panel$Acronimo_t))

# add a column of 1s to the panel data
#hitters_panel <- cbind(hitters_panel, fa = rep(1, nrow(hitters_panel)))
#fielders_panel <- cbind(fielders_panel, fa = rep(1, nrow(fielders_panel)))

hitters_panel %>% count(Posicion_t, sort = TRUE)
fielders_panel %>% count(Posicion_t, sort = TRUE)

# split the data frame by category
split_hitter <- split(hitters_panel, f = hitters_panel$Posicion_t)
split_fielder <- split(fielders_panel, f = fielders_panel$Posicion_t)

# Whole panel:
# Offensive:
h_category_1 <- split_hitter[["SP"]]
h_category_2 <- split_hitter[["RP"]]
h_category_3 <- split_hitter[["RP/CL"]]
h_category_4 <- split_hitter[["C"]]
h_category_5 <- split_hitter[["1B"]]
h_category_6 <- split_hitter[["2B"]]
h_category_7 <- split_hitter[["3B"]]
h_category_8 <- split_hitter[["SS"]]
h_category_9 <- split_hitter[["RF"]]
h_category_10 <- split_hitter[["CF"]]
h_category_11 <- split_hitter[["LF"]]
d_hitter_data <- split_hitter[["DH"]]

# Defensive:
starting_data <- split_fielder[["SP"]]
b_category_2 <- split_fielder[["RP"]]
b_category_3 <- split_fielder[["RP/CL"]]
shorts_data <- split_fielder[["SS"]]

# All panels:
# Hitters:
# Concatenate the two categories
hitter_data <- rbind(h_category_1, h_category_2, h_category_3, h_category_4,
                     h_category_5, h_category_6, h_category_7, h_category_8,
                     h_category_9, h_category_10, h_category_11)
hitter_data <- unique(hitter_data)

# Fielders:
# Concatenate the two categories
relief_pitcher_data <- rbind(b_category_2, b_category_3)
relief_pitcher_data <- unique(relief_pitcher_data)

# LIsta de variables acumuladas y anualmente promediadas_
stat_hitter <- list("X_At_bats", "X_At_bats_2",
                    "X_Bateos", "X_Bateos_2",
                    "X_Bateos_promedio", "X_Bateos_promedio_2", 
                    "X_Dobles", "X_Dobles_2",
                    "X_Home_runs", "X_Home_runs_2",
                    "X_Ingresos_equipo", "X_Ingresos_equipo_2",
                    "X_Juegos_iniciados", "X_Juegos_iniciados_2",
                    "X_Porcentaje_On_base_plus_slugging", "X_Porcentaje_On_base_plus_slugging_2",
                    "X_Porcentaje_on_base", "X_Porcentaje_on_base_2",
                    "X_Porcentaje_slugging", "X_Porcentaje_slugging_2",
                    "X_Runs_batted_in", "X_Runs_batted_in_2",
                    "X_Triples", "X_Triples_2",
                    "X_WAR", "X_WAR_2")

# Add suffix "_t" to each name
stat_hitter_t <- paste0(stat_hitter, "_t")
stat_hitter_t_1 <- paste0(stat_hitter, "_t_1")

# LIsta de variables acumuladas y anualmente promediadas_
stat_fielder <- list('X_Bateos_2', 'X_Bateos',
                     'X_Carreras_2', 'X_Carreras_ganadas_2',
                     'X_Carreras_ganadas', 'X_Carreras',
                     'X_Comando_2', 'X_Comando',
                     'X_Control_2', 'X_Control',
                     'X_Dominio_2', 'X_Dominio',
                     'X_ERA_2', 'X_ERA',
                     "X_Ingresos_equipo", "X_Ingresos_equipo_2",
                     'X_Inning_pitched_2', 'X_Inning_pitched',
                     'X_Losses_2', 'X_Losses',
                     'X_Saves_2', 'X_Saves',
                     'X_Strike_outs_2', 'X_Strike_outs',
                     'X_WAR_2', 'X_WAR',
                     'X_WHIP_2', 'X_WHIP',
                     'X_Walks_2', 'X_Walks',
                     'X_Wins_2', 'X_Wins')

# Add suffix "_t" to each name
stat_fielder_t <- paste0(stat_fielder, "_t")
stat_fielder_t_1 <- paste0(stat_fielder, "_t_1")

# Control variables:
vars_ms  <- 'Y_Sueldo_regular_norm_t ~ I(Edad_t^2) + I(Anios_de_contrato_t^2) + I(team_num_t^2) + X_Ingresos_equipo_t + X_Ingresos_equipo_t_1 - 1'
vars_fe  <- 'Y_Sueldo_regular_norm_t ~ I(Edad_t^2) + I(Anios_de_contrato_t^2) + I(team_num_t^2) + X_Ingresos_equipo_t + X_Ingresos_equipo_t_1 - 1'

hitter_stats_1 = c("Edad$_{t}^2$", "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                   "$X_{AB_{t}}$","$X_{AB_{t-1}}$","$X_{AB^{2}_{t}}$","$X_{AB^{2}_{t-1}}$",
                   "$X_{H_{t}}$","$X_{H_{t-1}}$","$X_{H^{2}_{t}}$","$X_{H^{2}_{t-1}}$",
                   "$X_{BA_{t}}$","$X_{BA_{t-1}}$", "$X_{BA^{2}_{t}}$","$X_{BA^{2}_{t-1}}$",
                   "Agente$_{t}$")
hitter_stats_2 = c("Edad$_{t}^2$", "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                   "$X_{D_{t}}$","$X_{D_{t-1}}$","$X_{D^{2}_{t}}$","$X_{D^{2}_{t-1}}$",
                   "$X_{HR_{t}}$","$X_{HR_{t-1}}$","$X_{HR^{2}_{t}}$","$X_{HR^{2}_{t-1}}$",
                   "$X_{GS_{t}}$","$X_{GS_{t-1}}$", "$X_{GS^{2}_{t}}$","$X_{GS^{2}_{t-1}}$",
                   "Agente$_{t}$")
hitter_stats_3 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                   "$X_{OPS_{t}}$","$X_{OPS_{t-1}}$","$X_{OPS^{2}_{t}}$","$X_{OPS^{2}_{t-1}}$",
                   "$X_{OBP_{t}}$","$X_{OBP_{t-1}}$","$X_{OBP^{2}_{t}}$","$X_{OBP^{2}_{t-1}}$",
                   "$X_{SLG_{t}}$","$X_{SLG_{t-1}}$", "$X_{SLG^{2}_{t}}$","$X_{SLG^{2}_{t-1}}$",
                   "Agente$_{t}$")
hitter_stats_4 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                   "$X_{RBI_{t}}$","$X_{RBI_{t-1}}$","$X_{RBI^{2}_{t}}$","$X_{RBI^{2}_{t-1}}$",
                   "$X_{T_{t}}$","$X_{T_{t-1}}$","$X_{T^{2}_{t}}$","$X_{T^{2}_{t-1}}$",
                   "$X_{WAR_{t}}$","$X_{WAR_{t-1}}$", "$X_{WAR^{2}_{t}}$","$X_{WAR^{2}_{t-1}}$",
                   "Agente$_{t}$")
hitter_stats <- list(hitter_stats_1,
                     hitter_stats_2,
                     hitter_stats_3,
                     hitter_stats_4)

# Cycles for loop
hitter_rep <- 4
# Stats to show
hitter_stat_num <- 6

hitter_stats_long <- list(c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{AB_{t}}$","$X_{AB_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{AB^{2}_{t}}$","$X_{AB^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{H_{t}}$","$X_{H_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{H^{2}_{t}}$","$X_{H^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{BA_{t}}$","$X_{BA_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{BA^{2}_{t}}$","$X_{BA^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{D_{t}}$","$X_{D_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{D^{2}_{t}}$","$X_{D^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{HR_{t}}$","$X_{HR_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{HR^{2}_{t}}$","$X_{HR^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{GS_{t}}$","$X_{GS_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{GS^{2}_{t}}$","$X_{GS^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{OPS_{t}}$","$X_{OPS_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{OPS^{2}_{t}}$","$X_{OPS^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{OBP_{t}}$","$X_{OBP_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{OBP^{2}_{t}}$","$X_{OBP^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{SLG_{t}}$","$X_{SLG_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{SLG^{2}_{t}}$","$X_{SLG^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{RBI_{t}}$","$X_{RBI_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{RBI^{2}_{t}}$","$X_{RBI^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{T_{t}}$","$X_{T_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{T^{2}_{t}}$","$X_{T^{2}_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{WAR_{t}}$","$X_{WAR_{t-1}}$",
                            "Agente$_{t}$"),
                          c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                            "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                            "$X_{WAR^{2}_{t}}$","$X_{WAR^{2}_{t-1}}$",
                            "Agente$_{t}$")
                          )

fielder_stats_1 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                    "$X_{H^{2}_{t}}$","$X_{H^{2}_{t-1}}$","$X_{H_{t}}$","$X_{H_{t-1}}$",
                    "$X_{R^{2}_{t}}$","$X_{R^{2}_{t-1}}$","$X_{ER^{2}_{t}}$","$X_{ER^{2}_{t-1}}$",
                    "$X_{ER_{t}}$","$X_{ER_{t-1}}$", "$X_{R_{t}}$","$X_{R_{t-1}}$",
                    "Agente$_{t}$")
fielder_stats_2 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                    "$X_{Comando^{2}_{t}}$","$X_{Comando^{2}_{t-1}}$","$X_{Comando_{t}}$","$X_{Comando_{t-1}}$",
                    "$X_{Control^{2}_{t}}$","$X_{Control^{2}_{t-1}}$","$Control_{H_{t}}$","$X_{Control_{t-1}}$",
                    "$X_{Dominio^{2}_{t}}$","$X_{Dominio^{2}_{t-1}}$","$X_{Dominio_{t}}$","$X_{Dominio_{t-1}}$",
                    "Agente$_{t}$")
fielder_stats_3 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                    "$X_{ERA^{2}_{t}}$","$X_{ERA^{2}_{t-1}}$","$X_{ERA_{t}}$","$X_{ERA_{t-1}}$",
                    "$X_{IP^{2}_{t}}$","$X_{IP^{2}_{t-1}}$","$X_{IP_{t}}$","$X_{IP_{t-1}}$",
                    "$X_{L^{2}_{t}}$","$X_{L^{2}_{t-1}}$", "$X_{L_{t}}$","$X_{L_{t-1}}$",
                    "Agente$_{t}$")
fielder_stats_4 = c("$Edad_{t}$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                    "$X_{S^{2}_{t}}$","$X_{S^{2}_{t-1}}$","$X_{S_{t}}$","$X_{S_{t-1}}$",
                    "$X_{SO^{2}_{t}}$","$X_{SO^{2}_{t-1}}$","$X_{SO_{t}}$","$X_{SO_{t-1}}$",
                    "$X_{WAR^{2}_{t}}$","$X_{WAR^{2}_{t-1}}$","$X_{WAR_{t}}$","$X_{WAR_{t-1}}$",
                    "Agente$_{t}$")
fielder_stats_5 = c("Edad$_{t}^2$" , "Años contrato$_{t}^2$", "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                    "$X_{WHIP^{2}_{t}}$","$X_{WHIP^{2}_{t-1}}$","$X_{WHIP_{t}}$","$X_{WHIP_{t-1}}$",
                    "$X_{BB^{2}_{t}}$","$X_{BB^{2}_{t-1}}$","$X_{BB_{t}}$","$X_{BB_{t-1}}$",
                    "$X_{W^{2}_{t}}$","$X_{W^{2}_{t-1}}$","$X_{W_{t}}$","$X_{W_{t-1}}$",
                    "Agente$_{t}$")
fielder_stats <- list(fielder_stats_1,
                      fielder_stats_2,
                      fielder_stats_3,
                      fielder_stats_4,
                      fielder_stats_5)
# Cycles for loop
fielder_rep <- 5
# Stats to show
fielder_stat_num <- 6

fielder_stats_long <- list(c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{H^{2}_{t}}$","$X_{H^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{H_{t}}$","$X_{H_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{R^{2}_{t}}$","$X_{R^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{ER^{2}_{t}}$","$X_{ER^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{ER_{t}}$","$X_{ER_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{R_{t}}$","$X_{R_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Comando^{2}_{t}}$","$X_{Comando^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Comando_{t}}$","$X_{Comando_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Control^{2}_{t}}$","$X_{Control^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Control_{t}}$","$X_{Control_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Dominio^{2}_{t}}$","$X_{Dominio^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{Dominio_{t}}$","$X_{Dominio_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{ERA^{2}_{t}}$","$X_{ERA^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{ERA_{t}}$","$X_{ERA_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{IP^{2}_{t}}$","$X_{IP^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{IP_{t}}$","$X_{IP_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{L^{2}_{t}}$","$X_{L^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{DL_{t}}$","$X_{L_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{S^{2}_{t}}$","$X_{S^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{S_{t}}$","$X_{S_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{SO^{2}_{t}}$","$X_{SO^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{SO_{t}}$","$X_{SO_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{WAR^{2}_{t}}$","$X_{WAR^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{WAR_{t}}$","$X_{WAR_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{WHIP^{2}_{t}}$","$X_{WHIP^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{WHIP_{t}}$","$X_{WHIP_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{BB^{2}_{t}}$","$X_{BB^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{BB_{t}}$","$X_{BB_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{W^{2}_{t}}$","$X_{W^{2}_{t-1}}$",
                              "Agente$_{t}$"),
                            c("Edad$_{t}^2$","Años contrato$_{t}^2$",
                              "Equipo$_{t}^2$","X_Ingresos_equipo$_{t}$","X_Ingresos_equipo$_{t-1}$",
                              "$X_{W_{t}}$","$X_{W_{t-1}}$",
                              "Agente$_{t}$")
                            )

```
```{r}
names(hitters_panel)
```
```{r hitter_stimation_simple_pooling, echo=FALSE, eval=TRUE}
# Create a model to store the results
hitter_simple_pooling <- list()

# To store the results
hitter_results_simple_pooling_1 <- list()
hitter_results_simple_pooling_2 <- list()
hitter_results_simple_pooling_3 <- list()
hitter_results_simple_pooling_4 <- list()
hitter_results_simple_pooling <- list(result_1 = hitter_results_simple_pooling_1,
                                      result_2 = hitter_results_simple_pooling_2,
                                      result_3 = hitter_results_simple_pooling_3,
                                      result_4 = hitter_results_simple_pooling_4)

# Loop over the variables in var_hitter_list
for (j in 1:hitter_rep){
  
  for (i in 1:hitter_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_ms, stat_hitter_t[[i + hitter_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_hitter_t_1[[i + hitter_stat_num*(j - 1)]],
                     sep = " + ")
    
    hitter_simple_pooling[[i + hitter_stat_num*(j - 1)]] <- plm(formula, data = hitter_data,
                                                  model = "pooling",
                                                  index = c("id", "Anio_ref"))
        
    hitter_results_simple_pooling[[j]][[i]] <- coeftest(hitter_simple_pooling[[i + hitter_stat_num*(j - 1)]],
                                                        vcov = vcovHC(hitter_simple_pooling[[i + hitter_stat_num*(j - 1)]],
                                                                      type = "HC1",
                                                                      cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(hitter_results_simple_pooling[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Bateadores: Modelo Pooling",
          covariate.labels = hitter_stats[[j]])
}
```

### Starting pitcher

```{r starting_stimation_pooling, echo=FALSE, eval=TRUE}
# Create a model to store the results
fielder_simple_pooling <- list()

# To store the results
fielder_results_simple_pooling_1 <- list()
fielder_results_simple_pooling_2 <- list()
fielder_results_simple_pooling_3 <- list()
fielder_results_simple_pooling_4 <- list()
fielder_results_simple_pooling_5 <- list()
fielder_results_simple_pooling <- list(result_1 = fielder_results_simple_pooling_1,
                                       result_2 = fielder_results_simple_pooling_2,
                                       result_3 = fielder_results_simple_pooling_3,
                                       result_4 = fielder_results_simple_pooling_4,
                                       result_5 = fielder_results_simple_pooling_5)

# Loop over the variables in var_hitter_list
for (j in 1:fielder_rep){
  
  for (i in 1:fielder_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_ms, stat_fielder_t[[i + fielder_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_fielder_t_1[[i + fielder_stat_num*(j - 1)]],
                     sep = " + ")
    
    fielder_simple_pooling[[i + fielder_stat_num*(j - 1)]] <- plm(formula, data = starting_data,
                                                  model = "pooling",
                                                  index = c("id", "Anio_ref"))
        
    fielder_results_simple_pooling[[j]][[i]] <- coeftest(fielder_simple_pooling[[i + fielder_stat_num*(j - 1)]],
                                                         vcov = vcovHC(fielder_simple_pooling[[i + fielder_stat_num*(j - 1)]],
                                                                       type = "HC1",
                                                                       cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(fielder_results_simple_pooling[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Lanzadores Iniciales: Modelo Pooling",
          covariate.labels = fielder_stats[[j]])
}
```

## Efectos fijos

### Bateadores

Se obtendrán las estimaciones de las variables referentes a estadísticas deportivas sin controles

```{r hitter_stimation_simple_within, echo=FALSE, eval=TRUE}
# Create a model to store the results
hitter_simple_within <- list()

# To store the results
hitter_results_simple_within_1 <- list()
hitter_results_simple_within_2 <- list()
hitter_results_simple_within_3 <- list()
hitter_results_simple_within_4 <- list()
hitter_results_simple_within <- list(result_1 = hitter_results_simple_within_1,
                                      result_2 = hitter_results_simple_within_2,
                                      result_3 = hitter_results_simple_within_3,
                                      result_4 = hitter_results_simple_within_4)

# Loop over the variables in var_hitter_list
for (j in 1:hitter_rep){
  
  for (i in 1:hitter_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_fe, stat_hitter_t[[i + hitter_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_hitter_t_1[[i + hitter_stat_num*(j - 1)]],
                     sep = " + ")
    
    hitter_simple_within[[i + hitter_stat_num*(j - 1)]] <- plm(formula, data = hitter_data,
                                                  model = "within",
                                                  index = c("id", "Anio_ref"))
        
    hitter_results_simple_within[[j]][[i]] <- coeftest(hitter_simple_within[[i + hitter_stat_num*(j - 1)]],
                                                        vcov = vcovHC(hitter_simple_within[[i + hitter_stat_num*(j - 1)]],
                                                                      type = "HC1",
                                                                      cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(hitter_results_simple_within[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Bateadores: Estimador Within",
          covariate.labels = hitter_stats[[j]])
}
```

### Starting pitcher

```{r starting_stimation_within, echo=FALSE, eval=TRUE}
# Create a model to store the results
fielder_simple_within <- list()

# To store the results
fielder_results_simple_within_1 <- list()
fielder_results_simple_within_2 <- list()
fielder_results_simple_within_3 <- list()
fielder_results_simple_within_4 <- list()
fielder_results_simple_within_5 <- list()
fielder_results_simple_within <- list(result_1 = fielder_results_simple_within_1,
                                       result_2 = fielder_results_simple_within_2,
                                       result_3 = fielder_results_simple_within_3,
                                       result_4 = fielder_results_simple_within_4,
                                       result_5 = fielder_results_simple_within_5)

# Loop over the variables in var_hitter_list
for (j in 1:fielder_rep){
  
  for (i in 1:fielder_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_fe, stat_fielder_t[[i + fielder_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_fielder_t_1[[i + fielder_stat_num*(j - 1)]],
                     sep = " + ")
    
    fielder_simple_within[[i + hitter_stat_num*(j - 1)]] <- plm(formula, data = starting_data,
                                                  model = "within",
                                                  index = c("id", "Anio_ref"))
        
    fielder_results_simple_within[[j]][[i]] <- coeftest(fielder_simple_within[[i + fielder_stat_num*(j - 1)]],
                                                         vcov = vcovHC(fielder_simple_within[[i + fielder_stat_num*(j - 1)]],
                                                                       type = "HC1",
                                                                       cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(fielder_results_simple_within[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Lanzadores Iniciales: Estimador Within",
          covariate.labels = fielder_stats[[j]])
}
```

## Efectos aleatorios

### Bateadores

Se obtendrán las estimaciones de las variables referentes a estadísticas deportivas sin controles

```{r hitter_stimation_simple_random, echo=FALSE, eval=TRUE}
# Create a model to store the results
hitter_simple_random <- list()

# To store the results
hitter_results_simple_random_1 <- list()
hitter_results_simple_random_2 <- list()
hitter_results_simple_random_3 <- list()
hitter_results_simple_random_4 <- list()
hitter_results_simple_random <- list(result_1 = hitter_results_simple_random_1,
                                      result_2 = hitter_results_simple_random_2,
                                      result_3 = hitter_results_simple_random_3,
                                      result_4 = hitter_results_simple_random_4)

# Loop over the variables in var_hitter_list
for (j in 1:hitter_rep){
  
  for (i in 1:hitter_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_ms, stat_hitter_t[[i + hitter_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_hitter_t_1[[i + hitter_stat_num*(j - 1)]],
                     sep = " + ")
    
    hitter_simple_random[[i + hitter_stat_num*(j - 1)]] <- plm(formula, data = hitter_data,
                                                  model = "random",
                                                  index = c("id", "Anio_ref"))
        
    hitter_results_simple_random[[j]][[i]] <- coeftest(hitter_simple_random[[i + hitter_stat_num*(j - 1)]],
                                                        vcov = vcovHC(hitter_simple_random[[i + hitter_stat_num*(j - 1)]],
                                                                      type = "HC1",
                                                                      cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(hitter_results_simple_random[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Bateadores: Efectos Aleatorios",
          covariate.labels = hitter_stats[[j]])
}
```

### Starting pitcher

```{r starting_stimation_random, echo=FALSE, eval=TRUE}
# Create a model to store the results
fielder_simple_random <- list()

# To store the results
fielder_results_simple_random_1 <- list()
fielder_results_simple_random_2 <- list()
fielder_results_simple_random_3 <- list()
fielder_results_simple_random_4 <- list()
fielder_results_simple_random_5 <- list()
fielder_results_simple_random <- list(result_1 = fielder_results_simple_random_1,
                                       result_2 = fielder_results_simple_random_2,
                                       result_3 = fielder_results_simple_random_3,
                                       result_4 = fielder_results_simple_random_4,
                                       result_5 = fielder_results_simple_random_5)

# Loop over the variables in var_hitter_list
for (j in 1:fielder_rep){
  
  for (i in 1:fielder_stat_num){
    # Run linear regression with grouped errors by country and robust errors
    base_vars_h  <- paste(vars_ms, stat_fielder_t[[i + fielder_stat_num*(j - 1)]],
                        sep = '+')
    formula <- paste(base_vars_h,
                     stat_fielder_t_1[[i + fielder_stat_num*(j - 1)]],
                     sep = " + ")
    
    fielder_simple_random[[i + hitter_stat_num*(j - 1)]] <- plm(formula, data = starting_data,
                                                  model = "random",
                                                  index = c("id", "Anio_ref"))
        
    fielder_results_simple_random[[j]][[i]] <- coeftest(fielder_simple_random[[i + fielder_stat_num*(j - 1)]],
                                                         vcov = vcovHC(fielder_simple_random[[i + fielder_stat_num*(j - 1)]],
                                                                       type = "HC1",
                                                                       cluster = "group"))
  }
  
  # Print the third block of results
  stargazer(fielder_results_simple_random[[j]],
          no.space = TRUE,
          type = "latex",
          title = "Lanzadores Iniciales: Efectos Aleatorios",
          covariate.labels = fielder_stats[[j]])
}
```



# Comparación entre periodos

Obtendremos los estimadores para los primeros dos años de observación para luego compararlos con los estimadores para el resto de años. Primero, aseguremos que los páneles estén ordenados por nombre y año de referencia

```{r order_player_anio_ref}
# Sort dataframe by player name and year_ref
hitter_data <- hitter_data %>% arrange(Jugador, Anio_ref)
# Sort dataframe by player name and year_ref
starting_data <- starting_data %>% arrange(Jugador, Anio_ref)
```

```{r split_hitter_data_periods, include=FALSE}
# Split the data into two data frames
hitter_data_split <- hitter_data %>% 
                     group_split(Jugador) 

# Keep only the first two years in the first data frame
hitter_first_two <- hitter_data_split %>% 
                    lapply(function(x) if(nrow(x) >= 2) head(x, 2) else NULL) %>% 
                    bind_rows()

# Keep the remaining years in the second data frame
hitter_remaining <- hitter_data_split %>% 
                    lapply(function(x) if(nrow(x) > 2) tail(x, -2) else NULL) %>% 
                    bind_rows()
```

```{r split_fielder_data_periods, include=FALSE}
# Split the data into two data frames
starting_data_split <- starting_data %>% 
                      group_split(Jugador) 

# Keep only the first two years in the first data frame
starting_first_two <- starting_data_split %>% 
                      lapply(function(x) if(nrow(x) >= 2) head(x, 2) else NULL) %>% 
                      bind_rows()

# Keep the remaining years in the second data frame
starting_remaining <- starting_data_split %>% 
                      lapply(function(x) if(nrow(x) > 2) tail(x, -2) else NULL) %>% 
                      bind_rows()
```

Haremos las estimaciones con todos los modelos para obtener un análisis robusto


```{r hitter_var_list_aux, include=FALSE}
# LIsta de variables acumuladas y anualmente promediadas_
stat_hitter <- list("X_At_bats", "X_At_bats_2",
                    "X_Bateos", "X_Bateos_2",
                    "X_Bateos_promedio", "X_Bateos_promedio_2", 
                    "X_Dobles", "X_Dobles_2",
                    "X_Home_runs", "X_Home_runs_2",
                    "X_Juegos_iniciados", "X_Juegos_iniciados_2",
                    "X_Porcentaje_On_base_plus_slugging", "X_Porcentaje_On_base_plus_slugging_2",
                    "X_Porcentaje_on_base", "X_Porcentaje_on_base_2",
                    "X_Porcentaje_slugging", "X_Porcentaje_slugging_2",
                    "X_Runs_batted_in", "X_Runs_batted_in_2",
                    "X_Triples", "X_Triples_2",
                    "X_WAR", "X_WAR_2")

# Add suffix "_t" to each name
stat_hitter_t <- paste0(stat_hitter, "_t")
stat_hitter_t_1 <- paste0(stat_hitter, "_t_1")
```

```{r fielder_var_list_aux, include = FALSE}
# LIsta de variables acumuladas y anualmente promediadas_
stat_fielder <- list('X_Bateos_2', 'X_Bateos',
                     'X_Carreras_2', 'X_Carreras_ganadas_2',
                     'X_Carreras_ganadas', 'X_Carreras',
                     'X_Comando_2', 'X_Comando',
                     'X_Control_2', 'X_Control',
                     'X_Dominio_2', 'X_Dominio',
                     'X_ERA_2', 'X_ERA',
                     'X_Inning_pitched_2', 'X_Inning_pitched',
                     'X_Losses_2', 'X_Losses',
                     'X_Saves_2', 'X_Saves',
                     'X_Strike_outs_2', 'X_Strike_outs',
                     'X_WAR_2', 'X_WAR',
                     'X_WHIP_2', 'X_WHIP',
                     'X_Walks_2', 'X_Walks',
                     'X_Wins_2', 'X_Wins')

# Add suffix "_t" to each name
stat_fielder_t <- paste0(stat_fielder, "_t")
stat_fielder_t_1 <- paste0(stat_fielder, "_t_1")
```

## Pooling 

### Bateadores

```{r hitter_stimation_simple_pooling_fa, echo=FALSE, eval=TRUE}
# To store models
hitter_model_pooling_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_hitter_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_h  <- paste(vars_ms, stat_hitter_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_h,
                   stat_hitter_t_1[[i]],
                   sep = " + ")
  
  hitter_model_pooling_fa[[i]] <- plm(formula, data = hitter_first_two,
                                      model = "pooling",
                                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(hitter_model_pooling_fa[[i]],
                              vcov = vcovHC(hitter_model_pooling_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  h_m_pooled_f <- plm(formula, data = hitter_remaining,
                      model = "pooling",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(h_m_pooled_f,
                              vcov = vcovHC(h_m_pooled_f,
                                            type = "HC1",
                                            cluster = "group"))
  
  # To store models
  h_m_pooled <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(h_m_pooled,
            no.space = TRUE,
            type = "text",
           title = "Bateadores regulares: Efecto de la edad (Pooling)",
          column.labels = c("Primeros dos años", "Años restantes"),
         covariate.labels = hitter_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(hitter_model_pooling_fa[[i]],h_m_pooled_f))
}
```

### Starting pitcher

```{r starting_stimation_pooling_ini, echo=FALSE, eval=TRUE}
# To store models
fielder_model_pooling_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_fielder_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_s  <- paste(vars_ms, stat_fielder_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_s,
                   stat_fielder_t_1[[i]],
                   sep = " + ")
  
  fielder_model_pooling_fa[[i]] <- plm(formula, data = starting_first_two,
                                       model = "pooling",
                                       index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(fielder_model_pooling_fa[[i]],
                              vcov = vcovHC(fielder_model_pooling_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  s_m_pooled_f <- plm(formula, data = starting_remaining,
                      model = "pooling",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(s_m_pooled_f,
                              vcov = vcovHC(s_m_pooled_f,
                                            type = "HC1",
                                            cluster = "group"))
  # To store models
  s_m_pooled <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(s_m_pooled,
            no.space = TRUE,
            type = "text",
            title = "Lanzadores iniciales: Efecto de la edad (Pooling)",
            column.labels = c("Primeros dos años", "Años restantes"),
            covariate.labels = fielder_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(fielder_model_pooling_fa[[i]],s_m_pooled_f))
}
```

## Efectos fijos

### Bateadores

```{r hitter_stimation_simple_within_ini, echo=FALSE, eval=TRUE}
# To store results:
hitter_model_fe_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_hitter_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_h <- paste(vars_fe, stat_hitter_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_h,
                   stat_hitter_t_1[[i]],
                   sep = " + ")
  
  hitter_model_fe_fa[[i]] <- plm(formula, data = hitter_first_two,
                                  model = "within",
                                  index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(hitter_model_fe_fa[[i]],
                              vcov = vcovHC(hitter_model_fe_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))

  h_m_fix_ef_f <- plm(formula, data = hitter_remaining,
                      model = "within",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(h_m_fix_ef_f,
                              vcov = vcovHC(h_m_fix_ef_f,
                                            type = "HC1",
                                            cluster = "group"))
  
  # To store models
  h_m_fix_ef <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(h_m_fix_ef,
            no.space = TRUE,
            type = "text",
            title = "Bateadores regulares: Efecto de la edad (Within)",
            column.labels = c("Primeros dos años", "Años restantes"),
            covariate.labels = hitter_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(hitter_model_fe_fa[[i]],h_m_fix_ef_f))
}
```

### Starting pitcher

```{r starting_stimation_within_ini, echo=FALSE, eval=TRUE}
# To store results:
fielder_model_fe_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_fielder_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_s <- paste(vars_fe, stat_fielder_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_s,
                   stat_fielder_t_1[[i]],
                   sep = " + ")
  
  fielder_model_fe_fa[[i]] <- plm(formula, data = starting_first_two,
                                  model = "within",
                                  index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(fielder_model_fe_fa[[i]],
                              vcov = vcovHC(fielder_model_fe_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  s_m_fix_ef_f <- plm(formula, data = starting_remaining,
                      model = "within",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(s_m_fix_ef_f,
                            vcov = vcovHC(s_m_fix_ef_f,
                                          type = "HC1",
                                          cluster = "group"))
  
  # To store models
  s_m_fix_ef <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(s_m_fix_ef,
            no.space = TRUE,
            type = "text",
            title = "Lanzadores iniciales: Efecto de la edad (Within)",
            column.labels = c("Primeros dos años", "Años restantes"),
            covariate.labels = fielder_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(fielder_model_fe_fa[[i]],s_m_fix_ef_f))
}
```

## Efectos aleatorios

### Bateadores

```{r hitter_stimation_simple_random_ini, echo=FALSE, eval=TRUE}
# To store results:
hitter_model_random_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_hitter_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_h  <- paste(vars_ms, stat_hitter_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_h,
                   stat_hitter_t_1[[i]],
                   sep = " + ")
 
  hitter_model_random_fa[[i]] <- plm(formula, data = hitter_first_two,
                                     model = "random",
                                     index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(hitter_model_random_fa[[i]],
                              vcov = vcovHC(hitter_model_random_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  h_m_random_f <- plm(formula, data = hitter_remaining,
                      model = "random",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(h_m_random_f,
                              vcov = vcovHC(h_m_random_f,
                                            type = "HC1",
                                            cluster = "group"))
  
  # To store models
  h_m_random <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(h_m_random,
            no.space = TRUE,
            type = "text",
            title = "Bateadores regulares: Efecto de la edad (Random Effects)",
            column.labels = c("Primeros dos años", "Años restantes"),
            covariate.labels = hitter_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(hitter_model_random_fa[[i]],h_m_random_f))
}
```

### Starting pitcher

```{r starting_stimation_random_ini, echo=FALSE, eval=TRUE}
# To store results:
fielder_model_random_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_fielder_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_s  <- paste(vars_ms, stat_fielder_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_s,
                   stat_fielder_t_1[[i]],
                   sep = " + ")
  
  fielder_model_random_fa[[i]] <- plm(formula, data = starting_first_two,
                                      model = "random",
                                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(fielder_model_random_fa[[i]],
                              vcov = vcovHC(fielder_model_random_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  s_m_random_f <- plm(formula, data = starting_remaining,
                      model = "random",
                      index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(s_m_random_f,
                              vcov = vcovHC(s_m_random_f,
                                            type = "HC1",
                                            cluster = "group"))
  
  # To store models
  s_m_random_ef <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(s_m_random_ef,
            no.space = TRUE,
            type = "text",
            title = "Lanzadores iniciales: Efecto de la edad (Random Effects)",
            column.labels = c("Primeros dos años", "Años restantes")#,
            #covariate.labels = fielder_stats_long[[i]]
            )
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(fielder_model_random_fa[[i]],s_m_random_f))
}
```

## First Differences

### Bateadores

Se obtendrán las estimaciones de las variables referentes a estadísticas deportivas sin controles

```{r hitter_stimation_simple_fd_ini, echo=FALSE, eval=TRUE}
# To Store results:
hitter_model_fd_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_hitter_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_h  <- paste(vars_fe, stat_hitter_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_h,
                   stat_hitter_t_1[[i]],
                   sep = " + ")
  
  hitter_model_fd_fa[[i]] <- plm(formula, data = hitter_first_two,
                                 model = "fd",
                                 index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(hitter_model_fd_fa[[i]],
                              vcov = vcovHC(hitter_model_fd_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  h_m_first_d_f <- plm(formula, data = hitter_remaining,
                       model = "fd",
                       index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(h_m_first_d_f,
                              vcov = vcovHC(h_m_first_d_f,
                                            type = "HC1",
                                            cluster = "group"))
  # To store models
  h_m_first_d <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(h_m_first_d,
            no.space = TRUE,
            type = "text",
            title = "Bateadores regulares: Efecto de la edad (First Differences)",
            column.labels = c("Primeros dos años", "Años restantes")
            #, covariate.labels = hitter_stats_long[[i]]
            )
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(hitter_model_fd_fa[[i]],h_m_first_d_f))
}
```

### Starting pitcher

```{r starting_stimation_fd_ini, echo=FALSE, eval=TRUE}
# To Store results
fielder_model_fd_fa <- list()

# loop over the variables in var_hitter_list
for (i in 1:length(stat_fielder_t_1)){
  # run linear regression with grouped errors by country and robust errors
  base_vars_s  <- paste(vars_fe, stat_fielder_t[[i]],
                      sep = '+')
  formula <- paste(base_vars_s,
                   stat_fielder_t_1[[i]],
                   sep = " + ")
  
  fielder_model_fd_fa[[i]] <- plm(formula, data = starting_first_two,
                                  model = "fd",
                                  index = c("id", "Anio_ref"))
  
  my_lm_cluster_i <- coeftest(fielder_model_fd_fa[[i]],
                              vcov = vcovHC(fielder_model_fd_fa[[i]],
                                            type = "HC1",
                                            cluster = "group"))
  
  s_m_first_d_f <- plm(formula, data = starting_remaining,
                       model = "fd",
                       index = c("id", "Anio_ref"))
  
  my_lm_cluster_f <- coeftest(s_m_first_d_f,
                              vcov = vcovHC(s_m_first_d_f,
                                            type = "HC1",
                                            cluster = "group"))
  # To store models
  s_m_first_d <- list(my_lm_cluster_i,my_lm_cluster_f)
  
  # Print the third block of results
  stargazer(s_m_first_d,
            no.space = TRUE,
            type = "text",
            title = "Lanzadores iniciales: Efecto de la edad (First Differences)",
            column.labels = c("Primeros dos años", "Años restantes"),
            covariate.labels = fielder_stats_long[[i]])
  
  # Hausman test:
  print("")
  print("Test para cambio estructural entre periodos:")
  print(phtest(fielder_model_fd_fa[[i]],s_m_first_d_f))
}
```